MSOA domestic Electricity and Gas maps

### 2021-08-26 MSOA domestic Elec and Gas.Rmd
Adding in Overlay maps to all the MSOA dom maps

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Mapping the change from 2010 to 2019
```{r Creating the difference in MSOA mean dom elec consumption variable}
domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"),skip = 1)
domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv"))
domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_domelec)
merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
summary(merged_domelec)
```
```{r Mapping the MSOA difference in mean dom elec consumption}
merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")
```
### Mapping the Gas
####2019
```{r Loading in the MSOA gas consumption data}
# gas consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA Dom Gas csv/MSOA_GAS_2019.csv")
msoa_gasData <- readr::read_csv(inFile)
head(msoa_gasData)
```
```{r Mapping the gas consumption of the MSOAs}
msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
ggplot2::ggplot(msoa_merged_sf_domgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> Does this match to non-gas areas??

@@

```{r checkLeaflet}
# https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
library(leaflet)

@@

```{r mapDiffLeaflet, fig.cap="Change in mean domestic gas kWh/meter"}

>>>>

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Map with Overlay
```{r Check leaflet for dom elec consumption}
library(leaflet)

st_coord_sys <- st_crs(msoa_merged_sf)
st_coord_sys$epsg
#Current coor system 27700 Leaflet wants EPSG: 4326 so we need to transform

#Transforming the coord system
if(st_coord_sys$epsg !=4326){
  map_df_trans <- st_transform(msoa_merged_sf, "+proj=longlat +datum=WGS84")
  }
```
```{r Plotting leaflet dom elec consumption map}
qpal <- colorNumeric("Reds", map_df_trans$`Mean consumption (kWh per meter)`, n = 9)

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(`Mean consumption (kWh per meter)`),
              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD),

####Mapping the change from 2010 to 2019
```{r Creating the difference in MSOA mean dom elec consumption variable}
domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"),skip = 1)
domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv"))
domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_domelec)
merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
summary(merged_domelec)
```
```{r Mapping the MSOA difference in mean dom elec consumption}
merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")
```
####Map with Overlay
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

st_coord_sys <- st_crs(msoa_domelec20102019)
st_coord_sys$epsg
#Current coor system 27700 Leaflet wants EPSG: 4326 so we need to transform

#Transforming the coord system
if(st_coord_sys$epsg !=4326){
  map_df_trans <- st_transform(msoa_domelec20102019, "+proj=longlat +datum=WGS84")
  }
```
```{r Plotting leaflet for change in dom elec consumption map}
qpal <- colorNumeric("Reds", map_df_trans$domelec_diff, n = 9)

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(domelec_diff),
              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD),

```
### Mapping the Gas
####2019
```{r Loading in the MSOA gas consumption data}
# gas consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA Dom Gas csv/MSOA_GAS_2019.csv")
msoa_gasData <- readr::read_csv(inFile)
head(msoa_gasData)
```
```{r Mapping the gas consumption of the MSOAs}
msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
ggplot2::ggplot(msoa_merged_sf_domgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> Does this match to non-gas areas??

####Map with Overlay
```{r Check leaflet for dom gas consumption}
library(leaflet)

st_coord_sys <- st_crs(msoa_merged_sf_domgas)
st_coord_sys$epsg
#Current coor system 27700 Leaflet wants EPSG: 4326 so we need to transform

#Transforming the coord system
if(st_coord_sys$epsg !=4326){
  map_df_trans <- st_transform(msoa_merged_sf_domgas, "+proj=longlat +datum=WGS84")
  }
```
```{r Plotting leaflet dom gas consumption map}
qpal <- colorNumeric("Reds", map_df_trans$`Mean consumption (kWh per meter)`, n = 9)

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(`Mean consumption (kWh per meter)`),
              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD),

@@

```{r checkLeaflet for change in dom gas consumption}
# https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
library(leaflet)

@@

```{r Plotting leaflet chnage in dom gas consumption map}
